---
title: "Performing Search Queries with the Tradera API in R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Performing Search Queries with the Tradera API in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE}
library(TradeRa)
library(RCurl, warn.conflicts = FALSE)
library(xml2, warn.conflicts = FALSE)
library(tibble, warn.conflicts = FALSE)
library(tidyr, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)
library(rlang, warn.conflicts = FALSE)
```

# Introduction

This vignette will guide you through using the `Search()` function to interact with the Tradera API. The `Search()` function provides a simple interface to send search queries and fetch results in a structured data format, making it easier to work with in R.

# Prerequisites

To use the function, you will need:

* `AppId`: A numeric application ID for authentication with the Tradera API.
* `AppKey`: A character string representing the application key for API access.
* `RCurl`, `xml2`, `tibble`, `tidyr`, `dplyr` and `rlang` libraries installed in your R environment. These libraries handle API requests, parsing XML, and data manipulation.

# Limitations

The function returns only the first 50 results on Tradera for the given search query. Due to the limit on 100 calls to the Tradera API per day the results of the query are cached in the local environment.

# Usage

## Function Arguments

The function requires four arguments:

* AppId (numeric): The application ID provided by Tradera for API authentication.
* AppKey (character): The application key provided by Tradera for API authentication.
* orderBy (character): Specifies the order of search results. Acceptable values are:
  * Relevance: Orders results based on relevance to the search term.
  * PriceAscending: Orders results by price in ascending order.
  * PriceDescending: Orders results by price in descending order.
* query (character): The search term or query string used to find items on Tradera.

## Return Value

The function returns a data frame with the following columns:

* ShortDescription: A brief description of the item.
* LongDescription: A detailed description of the item.
* Price: The price or current bid for the item.
* ItemUrl: A URL to the item's listing on Tradera.

If no items are found, the function returns a data frame with the message "Nothing found!". If there is an issue with the API (e.g., no response), it returns "Internal Tradera error!".

# Example: Basic Search Query

Here’s an example of using the function to search for ["Huernia"](https://en.wikipedia.org/wiki/Huernia) on Tradera, with results ordered by relevance:

```{r}
# Define API credentials and search parameters
AppId <- 5228 # Fake AppId, replace with your actual AppId
AppKey <- "21d94819-b4d5-4f28-a26c-51fe79ca197f" # Fake AppKey, replace with your actual AppKey
query <- "Huernia"
orderBy <- "Relevance"

# Perform the search
result <- Search(AppId, AppKey, orderBy, query)

# Show the result
knitr::kable(head(result))
```

# Example: Ordering

To sort the results by price (ascending or descending), adjust the `orderBy` parameter:

```{r}  
# Sort results by price (descending)
result_by_desc <- Search(AppId, AppKey, "PriceDescending", "iPhone")

# Show the result
knitr::kable(head(result_by_desc, n = 1))
```

# Conclusion

The `Search()` function simplifies the process of interacting with the Tradera API, making it easy to search for items, retrieve results, and order them by relevance. By following the steps outlined in this vignette, you can efficiently search for and analyze Tradera listings in R.
